Word_freq

### 2021-09-09 word_freq.Rmd
smoothed counts and Childes words

#groups by sex and words(lower case) so now theres indevisual words with total count per gender. 
target_type_counts <- exc_target_types %>%
  filter(!is.na(target_child_sex)) %>%
  mutate(gloss = str_to_lower(gloss)) %>%
  group_by(language, gloss, target_child_sex) %>%
  summarise(count = sum(count))

@@

@@

# TODO: normalize counts (over CDI words or over all of CHILDES? per sex or joined?)
#re-summarizes by counts 
type_counts <- type_counts_mapped %>%
  group_by(target_child_sex, uni_lemma) %>%
  summarise(count = sum(count))

#finds missing items and makes their counts = 1
missing_items <- items_nested %>%
  filter(!(uni_lemma %in% type_counts$uni_lemma)) %>%
  select(uni_lemma) %>%
  mutate(female = 1, male = 1)

#adds back in the unfound words with count 1 and adds ones to all other words
type_counts_smoothed <- type_counts %>%
  mutate(count = count + 1) %>%
  pivot_wider(names_from = target_child_sex, values_from = count, values_fill = 1) %>%
  bind_rows(missing_items) %>%
  pivot_longer(cols = c(female, male), names_to = "sex", values_to = "count")

@@

# saveRDS(type_counts, "data/type_counts.rds")
# saveRDS(type_freqs, "data/type_freqs.rds")

>>>>

#groups by sex and words(lower case) so now theres individual words with total count per gender. 
target_type_counts <- exc_target_types %>%
  filter(!is.na(target_child_sex)) %>%
  mutate(gloss = str_to_lower(gloss)) %>%
  group_by(language, gloss, target_child_sex) %>%
  summarise(count = sum(count))
#stem childes words and get counts to use as recomended replacements

@@

#group stemmed words and counts
childes_replace <- type_counts_stemmed %>%
  group_by(gloss_stem, target_child_sex) %>%
  summarise(count = sum(count))

normalized_counts <- childes_replace %>%
  group_by(target_child_sex) %>%
  mutate(prob = count/sum(count), 
         count_per_mil =  prob * 1000000)

#totals of counts
total_counts <- childes_replace %>%
   group_by(target_child_sex) %>%
   summarize(count = sum(count))

@@

# TODO: normalize counts (over CDI words or over all of CHILDES? per sex or joined?)
#re-summarizes by counts 
type_counts <- type_counts_mapped %>%
  group_by(target_child_sex, uni_lemma) %>%
  summarise(count = sum(count))
  #1 is female 2 is male
  #mutate(count_per_mil = 1000000 * (count/ifelse(target_child_sex == "male", total_counts$count[2], total_counts$count[1])))

#finds missing items and makes their counts = 1
#missing mostly stared words like "penis*" and "church*"
missing_items <- items_nested %>%
  filter(!(uni_lemma %in% type_counts$uni_lemma)) %>%
  select(uni_lemma) %>%
  mutate(female = 1, male = 1)

#adds back in the unfound words with count 1 and adds ones to all other words
type_counts_smoothed <- type_counts %>%
  mutate(count = count + 1) %>%
  pivot_wider(names_from = target_child_sex, values_from = count, values_fill = 1) %>%
  bind_rows(missing_items) %>%
  pivot_longer(cols = c(female, male), names_to = "sex", values_to = "count") %>%
  #1 is female 2 is male
  mutate(count_per_mil = 1000000 * (count/ifelse(sex == "male", total_counts$count[2], total_counts$count[1])))

@@

# saveRDS(type_counts, "data/type_counts.rds")
# saveRDS(type_freqs, "data/type_freqs.rds")
#saveRDS(normalized_counts, "data/normalized_childes_counts.rds")
#saveRDS(type_counts_smoothed, "data/type_counts_smoothed.rds")
